Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-11 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Add text to paper draft

>>>>

Flash floods cause most of the flood-related deaths in the eastern US [@Ashley2008], and one study found that most flash flooding in the eastern half of the US results from extreme rainfall over a period of six hours or less [@Ashley2008], which suggests that are exposure window of the three days around a storm may be wide enough to capture the most dangerous exposures.
